ngth{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
% \titleformat{\section}{
%   \vspace{-4pt}\scshape\raggedright\large
%   }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%
%   % Ensure that generate pdf is machine readable/ATS parsable
%   \pdfgentounicode=1
%
%   %-------------------------
%   % Custom commands
%   \newcommand{\resumeItem}[1]{
%     \item\small{
%         {#1 \vspace{-2pt}}
%           }
%           }
%
%           \newcommand{\resumeSubheading}[4]{
%             \vspace{-2pt}\item
%                 \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%                       \textbf{#1} & #2 \\
%                             \textit{\small#3} & \textit{\small #4} \\
%                                 \end{tabular*}\vspace{-7pt}
%                                 }
%
%                                 \newcommand{\resumeSubSubheading}[2]{
%                                     \item
%                                         \begin{tabular*}\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% Font options
% Using default Computer Modern font (serif) to match professional resume style
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtole{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{0.5em}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Alamin Mahamud} \\ \vspace{1pt}
    \small +880-168-7060-434 $|$ \href{mailto:hello@alamin.rocks}{\underline{hello@alamin.rocks}} $|$
    % \href{https://alamin.rocks}{\underline{alamin.rocks}} $|$
    \href{https://www.linkedin.com/in/alamin-mahamud}{\underline{linkedin.com/in/alamin-mahamud}} $|$
    \href{https://github.com/alamin-mahamud/}{\underline{github.com/alamin-mahamud}} 
    
\end{center}


%-- 

%--Enterprise-grade operator who led SOC 2 compliance initiatives, unlocking $50M+ in enterprise revenue through improved security posture and operational maturity.
%--Global technical leader and mentor, having mentored 50+ engineers into senior roles, contributed to open source, spoken at industry events, and supported products with 2M+ MAU and 100K+ user reviews.
%-- , while driving \textbf{\$1M+ in infrastructure cost optimization}.

%-----------SUMMARY-----------
\section{Executive Summary}
\resumeItemListStart
\resumeItem{\textbf{Platform \& SRE Architect} with \textbf{10+ years} delivering mission-critical infrastructure across on-prem, hybrid, and multi-cloud environments. Maintained \textbf{99.99\% uptime} for platforms serving \textbf{2M+ MAU} and supporting \textbf{\$60M+ Critical Infra}.}

\resumeItem{\textbf{Business impact leader} driving \textbf{\$1M+ annual cost optimization} and enabling \textbf{\$20M+ ARR growth}.}

\resumeItem{\textbf{Scale \& Reliability specialist} operating globally distributed DNS infrastructure handling \textbf{15B+ queries/month} with \textbf{1.5B+ malicious domains blocked}. Expert in ultra-low latency systems, distributed resilience, and large-scale threat mitigation.}

\resumeItem{\textbf{Technical depth} across \textbf{AWS, Kubernetes, Terraform, Python, Go, Prometheus, Grafana, and GitOps}. Proven track record building observability platforms, automating operations, and designing for security-first principles.}

\resumeItem{\textbf{Global operator} with cross-cultural leadership experience across \textbf{Bangladesh, USA, and Turkey}. Combines elite technical execution with executive business fluency—translating infrastructure decisions into revenue impact and strategic advantage.}

  % \resumeItem{\textbf{Platform, Cloud \& SRE Architect} with \textbf{10+ years} designing and operating across on-prem, hybrid, and cloud-native environments. Delivered \textbf{99.99\% uptime}, supporting \textbf{2M+ MAU}, and \textbf{\$60M+ critical platforms}.}
  % \resumeItem{\textbf{Scale \& reliability leader}, architecting globally distributed DNS systems serving \textbf{15B+ queries per month} and actively \textbf{blocking 1.5B+ malicious and harmful domains}. Designed systems focused on ultra-low latency, resilience, and large-scale abuse prevention.}
    
  % \resumeItem{\textbf{Business-driven infrastructure leader} who delivered \textbf{\$1M+ USD} annual savings, and supported the increase of \textbf{Annual Recurring Revenue (ARR)} upto \textbf{\$20M+}, Successfully extended the financial runway of a high-growth billion dollar trajectory startup by \textbf{4 months} through aggressive FinOps, switching to hybrid setup, reliability improvements, and infrastructure optimization.}
  % \resumeItem{\textbf{Hands-on DevOps/SRE leader} with deep expertise in \textbf{AWS, Kubernetes, Terraform, Python, Go, Prometheus, Grafana, Loki, and distributed systems}.}


  % \resumeItem{\textbf{Emerging tech entrepreneur \& angel investor} transitioning from operator to founder-invested \textbf{\$200K across 2 startups}, actively building a \textbf{\$60M Halal Ecosystem} for \textbf{\$2B+ Muslims}.}

  % \resumeItem{\textbf{Unique value proposition}: rare combination of \textbf{elite technical depth}, \textbf{security-first infrastructure thinking}, and \textbf{executive business fluency} (strategy, sales, FinOps), paired with a \textbf{global operating perspective} (\textbf{Bangladesh $\rightarrow$ USA $\rightarrow$ Turkey})—positioned to lead platform engineering at hypergrowth companies or build a next-generation infrastructure company.}


  %--\resumeItem{\textbf{Global platform engineer, mentor, and community builder} with experience operating across regions. Mentored \textbf{50+ engineers} into senior roles, active open-source contributor, conference speaker, and creator behind products with \textbf{100K+ user reviews} and an audience of \textbf{1K+ platform engineers}.}
  %-- \resumeItem{\textbf{Security \& threat intelligence expert} experienced in building \textbf{automated, centralized threat intelligence platforms} that detect and block malicious actors across \textbf{multi-hybrid, multi-region architectures}, integrating real-time signals into DNS, network, and application layers.}

  
\resumeItemListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior DevOps Engineer}{Aug. 2025 -- Present}
      {Kahf Yazılım A.Ş.}{Dhaka, Bangladesh (Hybrid)}
      \resumeItemListStart
      \resumeItem{\textbf{Architected and scaled DNS filtering infrastructure} serving \textbf{15B+ queries/month} across \textbf{3 regions}, blocking \textbf{1.5B+ malicious domains} and protecting \textbf{2M+ MAU}. Achieved sub-millisecond cache latency—\textbf{outperforming Google Public DNS}—through custom dnsdist and infra optimization.}

      \resumeItem{\textbf{Driving 62.5\% cost reduction (\$145k+ annually)} through strategic cloud exit—migrating 100\% Azure workloads to bare-metal infrastructure while \textbf{improving latency by 83\%}, via data-driven cost-benefit analysis and \textbf{state of the art monitoring system}.}
    
      \resumeItem{\textbf{Business development \& enterprise partnerships}: Onboarded \textbf{3 ISPs} for nationwide safe internet deployment. Leading technical discussions with mobile network operators and cloud vendors for multi-region expansion across Asia and Middle East.}
    
      \resumeItem{\textbf{Extended startup runway by 4 months} through aggressive infrastructure optimization, hybrid architecture design, and FinOps initiatives—critical impact for high-growth trajectory.}
    
      \resumeItem{\textbf{Built enterprise-grade observability platform} across 3 regions using Prometheus, Grafana, and Loki. Designed automated alerting, capacity planning dashboards, and real-time threat intelligence systems for 1.6M+ domain dataset.}
    
      \resumeItem{\textbf{Tech Stack}: Kubernetes, Terraform, Python, DNSDist,  Prometheus, Grafana, Loki, Ansible, Azure, Traefik, Helm, HAProxy}
        % \resumeItem{\textbf{Leading mission-critical infrastructure transformation} to make the online world safe \& secure, architecting next-generation security solutions for enterprise-scale operations.}
        % \resumeItem{\textbf{Spearheading complete cloud exit strategy}, migrating \textbf{100\% of infrastructure from Azure to bare-metal}, projected to \textbf{reduce operational costs by 65\%} (\$800K+ annually) while improving performance by 40\% through strategic infrastructure modernization.}
        % \resumeItem{\textbf{Championed cross-team collaboration} by conducting comprehensive cost-benefit analysis and presenting data-driven migration roadmap to C-suite executives, securing \textbf{\$2M+ infrastructure investment} approval.}
        % \resumeItem{\textbf{Technologies \& Skills}: Bind9, CloudNative-PG, Kubernetes, Ansible, Terraform, Microsoft Azure, Traefik, Helm Charts, Prometheus, Grafana, Loki}
      \resumeItemListEnd

    \resumeSubheading
      {Senior DevOps Engineer - Part Time}{May 2025 -- Jul. 2025}
      {Kahf Yazılım A.Ş.}{Istanbul, Turkey (Remote)}
      \resumeItemListStart
        \resumeItem{\textbf{Architecting hybrid cloud-to-bare-metal migration patterns}, documenting best practices and automation scripts that \textbf{reduced migration complexity by 70\%} for enterprise teams.}
        \resumeItem{\textbf{Technologies \& Skills}: Kubernetes, Ansible, Terraform, Microsoft Azure, Traefik, Helm Charts, Prometheus, Grafana, Loki}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer - AI Products - Part Time}{May 2025 -- Jul. 2025}
      {LeadSync.AI}{Singapore (Remote)}
      \resumeItemListStart
        \resumeItem{\textbf{Executed the product vision of AI-powered sales intelligence platform}, then \textbf{accelerated time-to-market by 40\%} by architecting end-to-end MCP integration with LLMs, directly contributing to \textbf{\$500k Seed funding} validation.}
        \resumeItem{\textbf{Technologies \& Skills}: MCP Protocol, LLM Integration, AI-SDK, TypeScript, PostgreSQL, Nest.JS, Next.JS}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Platform Engineer \& SRE -- Cloud Team}{Feb. 2022 -- Jan. 2025}
      {BriteCore Inc}{Springfield, MO, USA}
      \resumeItemListStart
        \resumeItem{\textbf{Generated \$20M+ ARR} by designing, implementing, and maintaining highly available, cost-efficient SaaS platforms.}
        \resumeItem{\textbf{Cut \$1M+ in cloud spend} by spearheading cloud cost-optimization initiatives across production workloads.}
        \resumeItem{\textbf{Eliminated 30\% of production brownouts} by optimizing runtime configuration and improving state management.}
        \resumeItem{\textbf{Accelerated development cycles by \textasciitilde35\%} by engineering CI/CD pipelines using GitHub Actions self-hosted runners, enabling 200+ daily builds.}
        \resumeItem{\textbf{Achieved SOC2 compliance} by reducing vulnerability exposure by \textasciitilde60\% through robust security controls and passing all external audits on the first attempt.}
        \resumeItem{\textbf{Neutralized large-scale DDoS attacks} through proactive monitoring and advanced filtering, blocking thousands of malicious requests per day while reducing brownouts.}
        \resumeItem{\textbf{Streamlined infrastructure provisioning by 80\%} by leveraging reusable Terraform modules and shared libraries.}
        \resumeItem{\textbf{Enhanced production visibility} by reducing mean time to detect (MTTD) by 80\% using real-time Datadog operational dashboards.}
        
      \resumeItemListEnd

    \resumeSubheading
      {Platform Engineer - Platform \& Cloud Team}{Apr. 2021 -- Jan. 2022}
      {BriteCore Inc}{Springfield, MO, USA}
      \resumeItemListStart
        \resumeItem{\textbf{Reduced AWS cloud costs by \textasciitilde\$36.5K annually} by optimizing CloudWatch log ingestion and retention strategies.}
        \resumeItem{\textbf{Mitigated data breach risk and multi-million dollar churn} by strengthening client data security with a cross-account read replica architecture.}
        \resumeItem{\textbf{Improved platform scalability and maintainability by 40\%} by leading cross-functional teams to design and deliver DevOps tooling, sustaining 99.99\% uptime across environments.}
        \resumeItem{\textbf{Accelerated go-to-market timelines by \textasciitilde30\%} and improved application performance by \textasciitilde15\% through deep root-cause analysis and targeted cross-team fixes.}
        \resumeItem{\textbf{Engineered a robust Data Abstraction Layer (DAL)} by integrating staged deployments across a multi-org AWS setup, enabling observability queries across 50+ accounts and near-instant production cloning for 24/7 support.}
        
      \resumeItemListEnd

    \resumeSubheading
      {Site Reliability Engineer - SRE \& SysOps Team}{Sep. 2019 -- Mar. 2021}
      {BriteCore Inc}{Springfield, MO, USA}
      \resumeItemListStart
        \resumeItem{\textbf{Maintained 99.99\% SLA for 50+ clients} by implementing advanced monitoring, proactive alerting, and customer-impact-driven SLOs.}
        \resumeItem{\textbf{Eliminated 30 minutes of recurring downtime} by implementing blue/green deployments and enabling zero-downtime production releases.}
        \resumeItem{\textbf{Improved internal team satisfaction by 20\%} by enabling custom production data selection at application startup.}
        \resumeItem{\textbf{Reduced operational toil by 75\%} by automating support workflows with a serverless nightly release reporting system.}
        \resumeItem{\textbf{Increased enterprise customer satisfaction to 90\%} by enabling continuous delivery across multiple release cadences.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{May 2019 -- Jul. 2019}
      {Pathao LLC}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{\textbf{Migrated 2M user ratings with zero data loss} by architecting and deploying a scalable feedback system.}
        \resumeItem{Standardized API structure by bootstrapping a robust API aggregation service.}
        \resumeItem{Optimized order invoicing by authoring a stateless microservice to calculate invoice amounts accurately.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Apr. 2018 -- Apr. 2019}
      {Portonics LLC}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{\textbf{Sustained 99.99\% uptime for 1M+ daily users} for high-traffic applications with \textbf{1M+ daily hits} by restructuring the underlying infrastructure.}
        \resumeItem{\textbf{Reduced page load times by 90\%} by implementing robust caching mechanisms and fallback support.}
        \resumeItem{\textbf{Enabled EMI features} in the payment module by integrating with a secure, efficient payment gateway.}
        \resumeItem{Expanded system scalability for a nationwide distribution network by decoupling a monolithic architecture into microservices, load-balancing traffic, and deploying read-write database replicas.}
        \resumeItem{Enhanced shopping experience for users by developing innovative features like \textbf{"cancel and re-order"} and \textbf{"coupon refund"}.}
      \resumeItemListEnd

    \resumeSubheading
      {Jr. Software Engineer}{Dec. 2017 -- Mar. 2018}
      {Cookups LLC}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Streamlined promotional workflows by integrating enhanced promo code generation, location management, and commission management systems.}
        \resumeItem{Developed a messenger bot that can automate customer interactions for their delivery service.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Expertise \& Core Competencies}

\textbf{Cloud \& DevOps Engineering}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Cloud Platforms} $|$ 
     \emph{AWS, Azure}}{}
  \resumeProjectHeading
    {\textbf{Infrastructure \& Automation} $|$ 
     \emph{Terraform, Ansible, CloudFormation, SaltStack}}{}
  \resumeProjectHeading
    {\textbf{CI/CD} $|$ 
     \emph{GitHub Actions, Gitlab}}{}
\resumeSubHeadingListEnd

\textbf{SaaS Architecture \& Platform Engineering}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Application Development} $|$ 
     \emph{Python, Go, TypeScript; FastAPI, NestJS, Gin, Flask, Django; REST, gRPC; JWT}}{}
  \resumeProjectHeading
    {\textbf{Data \& Messaging} $|$ 
     \emph{PostgreSQL, MySQL, Redis; RabbitMQ; Elasticsearch / OpenSearch}}{}
\resumeSubHeadingListEnd

\textbf{Linux Systems \& Performance Engineering}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Operating Systems} $|$ 
     \emph{Debian (Ubuntu, Kali), Arch Linux}}{}
  \resumeProjectHeading
    {\textbf{Kernel \& Performance} $|$ 
     \emph{sysctl, cgroups, eBPF; perf, strace, lsof, iostat, htop, sar}}{}
  \resumeProjectHeading
    {\textbf{Storage \& Security} $|$ 
     \emph{LVM, RAID, ZFS; SELinux, AppArmor, iptables, auditd, Fail2Ban}}{}
\resumeSubHeadingListEnd


\textbf{On-Prem Infrastructure \& Homelab}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Virtualization \& Storage} $|$ 
     \emph{Proxmox; TrueNAS, Ceph, ZFS, NFS}}{}
  \resumeProjectHeading
    {\textbf{Networking \& Automation} $|$ 
     \emph{pfSense, VLANs, VPN; Ansible-driven self-hosting,OSI, IPv6, DNS, TLS, Firewalls, BGP}}{}
\resumeSubHeadingListEnd


\textbf{Kubernetes Platform Engineering}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Containers \& Orchestration} $|$ 
     \emph{Docker, containerd, LXC; Kubernetes, ECS, EKS}}{}
  \resumeProjectHeading
    {\textbf{Cluster \& Networking} $|$ 
     \emph{kubeadm, MetalLB; Calico; VXLAN / IPIP}}{}
  \resumeProjectHeading
    {\textbf{Ingress, Storage \& GitOps} $|$ 
     \emph{Nginx, Traefik, Istio; Longhorn; Helm, Kustomize; ArgoCD}}{}
\resumeSubHeadingListEnd


\textbf{Kubernetes Development}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Controller \& Operator Development} $|$ 
     \emph{Kubernetes APIs, CRDs, Operators; Kubebuilder}}{}
  \resumeProjectHeading
    {\textbf{Golang Tooling} $|$ 
     \emph{client-go, controller-runtime, apimachinery}}{}
  \resumeProjectHeading
    {\textbf{Security \& Testing} $|$ 
     \emph{mTLS; kubectl-debug, k9s}}{}
\resumeSubHeadingListEnd


\textbf{Observability \& Security}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Monitoring \& Logging} $|$ 
     \emph{Datadog, CloudWatch, Prometheus, Grafana, Loki; ELK Stack}}{}
  \resumeProjectHeading
    {\textbf{Security \& Compliance} $|$ 
     \emph{SOC 2, OWASP; DDoS protection}}{}
\resumeSubHeadingListEnd

% \textbf{Cloud \& DevOps Engineering}
% \resumeSubHeadingListStart
%   \resumeProjectHeading
%     {\textbf{Multi-Cloud Architecture} $|$ 
%      \emph{AWS, Azure, Terraform, CloudFormation, Ansible}}{}
%   \resumeProjectHeading
%     {\textbf{K8s Platform Engineering} $|$ 
%      \emph{Kubernetes, Docker, Containerd, Helm}}{}
%   \resumeProjectHeading
%     {\textbf{Cloud Native Ecosystem} $|$ 
%      \emph{Prometheus, Grafana, Cilium, Istio, ArgoCD, Crossplane}}{}
%   \resumeProjectHeading
%     {\textbf{CI/CD \& Automation} $|$ 
%      \emph{GitHub Actions, Jenkins, Tekton, GitOps, ArgoCD}}{}
% \resumeSubHeadingListEnd

% \textbf{SaaS Architecture \& Development}
% \resumeSubHeadingListStart
%   \resumeProjectHeading
%     {\textbf{Backend Engineering} $|$ 
%      \emph{Python, Go, TypeScript, FastAPI, Nest.JS, Gin, Django, Flask}}{}
%   \resumeProjectHeading
%     {\textbf{Database \& Data Architecture} $|$ 
%      \emph{PostgreSQL, MySQL, Redis, Elasticsearch, OpenSearch}}{} % {8+ Years}
% \resumeSubHeadingListEnd


% \textbf{System Administration, Networking \& Security}
% \resumeSubHeadingListStart
%   \resumeProjectHeading
%     {\textbf{Linux Kernel \& Performance} $|$ 
%      \emph{eBPF, sysctl, cgroups, perf, ZFS, LVM}}{} %{4+ Years}
%   \resumeProjectHeading
%     {\textbf{Network Architecture} $|$ 
%      \emph{BGP, VXLAN, VPN, DNS, TLS, OSI Model, Firewalls}}{}%{2+ Years}
% \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chittagong University of Engineering \& Technology}{Chittagong, Bangladesh}
      {Bachelor of Science in Mechanical Engineering | CGPA: 3.24/4.00}{Mar. 2013 -- Sep. 2017}
      \resumeItemListStart
        \resumeItem{\textbf{Pivoted from mechanical to software engineering} during sophomore year, recognizing exponential growth potential in cloud computing and identifying personal aptitude for systems thinking and automation.}
        \resumeItem{\textbf{Founded university's Code Club} with 50+ members, organizing workshops on competitive programming that trained 200+ students and established foundation for tech entrepreneurship journey.}
        \resumeItem{\textbf{Undergraduate Research}: Automation of three wheeler vehicles registration by number plate.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------AWARDS-----------
\section{Awards \& Recognition}
  \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{International Engineering Innovation Summit 2015}}{Dhaka, Bangladesh}
          \resumeItemListStart
            \resumeItem{\textbf{Hackathon Champion (1st Place, 10+ teams)}}
            \resumeItem{\textbf{App Fest Runner-Up}}
          \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------COMMUNITY ENGAGEMENT-----------
\section{Community Engagement \& Thought Leadership}
  \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{Technical Content \& Thought Leadership}}{2022 -- Present}
          \resumeItemListStart
            \resumeItem{\textbf{LinkedIn (1K+ followers)}: Recognized gap in practical DevOps content, shifted from theoretical tutorials to real-world war stories—posts reach 50K+ monthly impressions, establishing personal brand as infrastructure innovator.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Mentorship \& Community Building}}{2021 -- Present}
          \resumeItemListStart
            \resumeItem{\textbf{1-on-1 Mentorship}: Mentor 20+ junior engineers quarterly, focusing on career acceleration in cloud/AI—mentees.}
            \resumeItem{\textbf{Motivation}: Having benefited from open-source community, committed to "paying it forward" by democratizing infrastructure knowledge and creating opportunities for underrepresented engineers.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Angel Investing \& Startup Advisory}}{2024 -- Present}
          \resumeItemListStart
            \resumeItem{\textbf{Strategic pivot to investor}: Transitioned from operator to investor, recognizing pattern-matching ability from scaling 50+ production systems—invested in 2 startups (\textbf{\$200K total investment committed}).}
            \resumeItem{\textbf{Investment Thesis}: Focus on DevOps automation, AI infrastructure, and FinOps tools—targeting 10x returns while solving real engineering pain points experienced firsthand.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RECOMMENDATIONS-----------
\section{Professional Recommendations}
  \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Omar Faruque Tuhin} $|$ \emph{Staff Software Engineer at Pathao}}{Apr. 2025}
          \resumeItemListStart
            \resumeItem{"I had the privilege of mentoring him during his 2018 internship where he worked with Django REST Framework. Even then, he stood out for his technical prowess, problem-solving skills, and ability to deliver production-ready solutions. His curiosity and dedication to mastering complex concepts were truly impressive. \textbf{Watching his career evolve has been rewarding - from a promising intern to a technology leader architecting scalable cloud platforms that drive real business impact}. His unique blend of technical expertise and strategic vision makes him an invaluable asset to any organization."}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Sian Lerk Lau} $|$ \emph{Senior Software Engineer/Technical Services Lead at BriteCore}}{Jan. 2025}
          \resumeItemListStart
            \resumeItem{"It was pleasant working with Alamin at BriteCore. As a Senior Site Reliability Engineer, he brought not only exceptional skills in platform architecture, AWS, and IaC, but also a genuine passion for building systems that are reliable, secure, and efficient. \textbf{Alamin has a rare ability to tackle complex challenges with calm confidence}. Whether improving platform stability, streamlining deployments, or strengthening security, he always found solutions that balanced technical excellence with practical impact. What truly stood out was his generosity in sharing knowledge and supporting his teammates. \textbf{He's the kind of colleague who makes everyone better}, simply by how he approaches problems and treats people."}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Sunny Parekh} $|$ \emph{Director of Information Security, Technology and Compliance at BriteCore}}{May 2025}
          \resumeItemListStart
            \resumeItem{"I've had the pleasure of working with Alamin, whose expertise in building cloud-driven SaaS platforms is impressive. \textbf{Alamin has guided DevOps efforts with a focus on scalability, functionality, and efficiency}. Alamin is a reliable, forward-thinking professional who delivers real business impact through technology."}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Ariful Islam} $|$ \emph{Principal Software Engineer at Brain Station 23}}{Jun. 2019}
          \resumeItemListStart
            \resumeItem{"It is rare that you come across a person like Alamin Mahamud. I have known him since 2014. \textbf{He has transformed himself from a Mechanical Engineer to a professional Software Engineer}. He has built a reputation in the dev community with his broad vision. Apart from developing skills he has exceptional communication skills and loves to read. He has been a very good friend of mine and I know how well grounded he is. I recommend Alamin Mahamud highly as I know that he will never let anyone down."}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Al Amin Ibne Mosaddeque Chayan} $|$ \emph{Principal Software Engineer at Portonics Limited}}{Jul. 2019}
          \resumeItemListStart
            \resumeItem{"Alamin was a fantastic person to work with, and is not only a multi-skilled and insightful colleague, but also an inspiring strategist. Very good person. \textbf{Great employee with a very strong problem solving skills. He is an asset to any company.}"}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Ahmed Shamim Hassan} $|$ \emph{Software Engineer at Kahf Yazılım A.Ş.}}{Jun. 2019}
          \resumeItemListStart
            \resumeItem{"I've known Alamin for quite some time. Even though we didn't work closely, still I figured out his enthusiasm about learning and experimenting with new stuff. We had chat over messaging apps, discussed things over the phone regularly about career, technology, etc. As soon as I had the chance to refer him to the Pathao I didn't wait a bit. I knew that he is the perfect guy to have in any fast growing team. \textbf{He is a real asset for any technology team}. I'm wishing for his success in every aspect of life."}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Sakibur Rahaman Chowdhury} $|$ \emph{Senior Software Engineer at Turing}}{Jun. 2019}
          \resumeItemListStart
            \resumeItem{"\textbf{Courage \& passion are the key elements Alamin possesses}. His dreams may be bigger than skies, but his hard-working mentality and passion towards CS will guide him to the pinnacle of success. All the best for his future endeavors."}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Md Shoeb Abdullah} $|$ \emph{Senior Golang Developer/Lead at Acore Health}}{Mar. 2019}
          \resumeItemListStart
            \resumeItem{"Thirst for new technologies made Md Alamin Mahmud ``Next Generation'' programmer to me. When Alamin is in your team, you know he will keep you up-to-date with upcoming technologies. He is also a Linux expert. If you want to find the most social and jolly person in the company, probably Alamin will be the one. \textbf{Finally, Alamin is a great motivation to me!}"}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Md. Jahangir Alam} $|$ \emph{Senior Software Engineer at Sulaco Tec}}{Jul. 2019}
          \resumeItemListStart
            \resumeItem{"I have had the opportunity to work with Md. Alamin Mahamud while working at Portonics Limited. He is quick learner, good team player and hard worker. He is a passionate developer to develop any projects by new technologies. He was very professional during developing any projects. I wish him all the best."}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}


    %                             }
    %       }
    % }
    %   }
  % }
